% vim: ft=tex fdm=marker et sts=2 sw=2 cole=0
%
% vitae.tex -- a minimalistic LaTeX template for resumes
%
% The design is intentionally minimalistic and I don't use
% LaTeX packages that are not part of the standard TeXLive
% distribution, and one should be able to distribute the
% entire resume as a single LaTeX file.  The styling and
% layout was partially inspired by Donald Knuth's CV [1].
%
% Copyright (c) 2014-2022, Manu Mannattil.
% All rights reserved.
%
% Usage, modification, and distribution of this document,
% for any purpose, with or without attribution, is permitted
% provided the author's personal/professional details are
% removed.
%
% [1] https://www-cs-faculty.stanford.edu/~knuth/vita.pdf
%

% Preamble {{{1
% -------------

\documentclass[10pt,a4paper,article,oneside]{memoir}

\def\fname{Manu Mannattil}                % Set your full name here.
\def\iname{M.~Mannattil}                  % Set your intials + last name here.
\def\bname{\underline{Manu Mannattil}}    % Set your name as you'd like it to appear in bibliographies.

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}

\setlrmarginsandblock{1.25in}{1.25in}{*}
\setulmarginsandblock{1.25in}{1.25in}{*}
\checkandfixthelayout

\usepackage{color}
\definecolor{bs1}{rgb}{0.207843,0.415686,0.623529}
\definecolor{gray}{rgb}{0.5,0.5,0.5}

\usepackage[
  allcolors=bs1,
  colorlinks=true,
  pdftex,
  pdfauthor={\fname},
  pdftitle={Curriculum Vitae: \fname},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={curriculum vitae, resume, vitae}
]{hyperref}
\urlstyle{same}

% Custom commands.
\def\email#1{\href{mailto:#1}{#1}}
\def\doi#1#2{\href{https://doi.org/#1}{#2}}
\def\arxiv#1#2{\href{https://arxiv.org/abs/#1}{arXiv:#1 [#2]}}

\usepackage{gentium}
\linespread{1.05}

% Section styling.
\setsecheadstyle{\bfseries}
\setbeforesecskip{1.25\baselineskip}
\setaftersecskip{0.37\baselineskip}
\setsubsecheadstyle{\itshape}
\setbeforesubsecskip{0.75\baselineskip}
\setaftersubsecskip{0.25\baselineskip}
\setcounter{secnumdepth}{0}

% From Section 3.5 of memoir's documentation.
\clubpenalty=9996
\widowpenalty=9999
\brokenpenalty=4991
\predisplaypenalty=10000
\postdisplaypenalty=1549
\displaywidowpenalty=1602

% Hanging paragraphs throughout.
\def\hangpars{%
  \leftskip=1.75em%
  \parindent=-\leftskip%
  \setsecindent{-\leftskip}%
  \setsubsecindent{-\leftskip}%
}

% Reset hanging paragraphs.
\def\nohangpars{%
  \leftskip=0pt%
  \parindent=0pt%
  \setsecindent{0pt}%
  \setsubsecindent{0pt}%
}

% Git commit info.
\ifdefined\gitInfo\else\def\gitInfo{.git/gitInfo.in}\fi
\IfFileExists{\gitInfo}{\input{\gitInfo}}{
  \def\gitError{$\heartsuit\heartsuit\heartsuit$}
  \def\gitHash{\gitError}
  \def\gitShortHash{\gitError}
  \def\gitRefName{\gitError}
  \def\gitAuthorName{\gitError}
  \def\gitAuthorEmail{\gitError}
  \def\gitAuthorDate{\gitError}
  \def\gitAuthorAltDate{\gitError}
  \def\gitCommitterName{\gitError}
  \def\gitCommitterEmail{\gitError}
  \def\gitCommitterDate{\gitError}
  \def\gitCommitterAltDate{\gitError}
}

\def\headerstyle#1{%
  \textls[120]{%
    \spaceskip=1.5\fontdimen2\font plus 1.5\fontdimen3\font minus 1.5\fontdimen4\font%
    \MakeUppercase{#1}%
  }%
}

% Header and footer.
\makeoddhead{headings}{}{\headerstyle{Curriculum {Vit\ae} --- \fname}}{}
\makeoddfoot{plain}{}{\headerstyle{\thepage}}{} % first page
\makeoddfoot{headings}{}{\headerstyle{\thepage}}{} % other pages
\pagestyle{headings}

\begin{document}

% Name and Contact Details {{{1
% -----------------------------

\thispagestyle{plain}
\hangpars

{\Large\headerstyle{CURRICULUM VIT\AE}}
\vskip2.25em

{\bfseries\large\fname}
\vskip1em

\begin{minipage}[t]{0.45\textwidth}
  \begin{tabular}{@{}l}
  School of Chemistry\\
  Tel Aviv University\\
  Tel Aviv 69978, Israel
  \end{tabular}
\end{minipage}
%
\begin{minipage}[b]{0.45\textwidth}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{@{}rl@{}}
    Phone: & (+1)~315-515-7373\\
    Email: & \email{manu.mannattil@posteo.net}\\
    \phantom{}
  \end{tabular}
\end{minipage}

% Personal Information {{{1
% -------------------------

\section{Personal Information}

Born on August 13, 1991 in Palakkad, Kerala; Indian citizen.

% Education {{{1
% --------------

\section{Education}

Syracuse University, Syracuse, New York, USA; August~2017--August 2023.\\
Ph.D. in Physics, August 2023; Dissertation: \emph{\href{https://raw.githubusercontent.com/manu-mannattil/thesis/build/thesis.pdf}{Asymptotics, Geometry, and Soft Matter}}.

Indian Institute of Technology Kanpur, Kanpur, Uttar Pradesh, India; July~2009--July~2014.\\
Integrated~M.Sc. in Physics, February~2015.

% Employment History {{{1
% -----------------------

\section{Employment History}

Postdoctoral Fellow, School of Chemistry, Tel Aviv University; October 2023--.

Research Assistant, Department of Physics, Syracuse University; May 2019--August 2023.

Teaching Assistant, Department of Physics, Syracuse University; August~2017--May 2019.

Project Associate, Nonlinear Dynamical Systems Group, Indian Institute of Technology Kanpur;\\ September 2014--October 2015.

% Publications {{{1
% -----------------

\section{Publications}

% \subsection{Works in progress}

% \begin{flexlabelled}{hfill}{1.5em}{*}{*}{2.5em}{*}
%   \setlength{\itemsep}{-0.25em}
%   \item[1.] {\bname}, ``Energy and Free-Energy Landscapes of Soft Few-Body Systems With Singular Constraints'', forthcoming.
% \end{flexlabelled}

%\subsection{Preprints}

%\begin{flexlabelled}{hfill}{1.5em}{*}{*}{2.5em}{*}
% \setlength{\itemsep}{-0.25em}
% \end{flexlabelled}

%\subsection{Refereed journal papers}

\begin{flexlabelled}{hfill}{1.5em}{*}{*}{2.5em}{*}
  \setlength{\itemsep}{0pt}
  \item[6.] {\bname} and Christian D.~Santangelo, ``Geometric Localization of Waves on Thin Elastic Structures'', \arxiv{2306.07213}{cond-mat.soft}.
  \item[5.] \bname, J.~M.~Schwarz, and Christian D.~Santangelo, ``Thermal Fluctuations of Singular Bar-Joint Mechanisms'', \doi{10.1103/PhysRevLett.128.208005}{Phys.~Rev.~Lett.~\textbf{128}, 208005 (2022)}, \arxiv{2112.04279}{cond-mat.soft}.
  \item[4.] \bname, Ambrish Pandey, Mahendra K.~Verma, and Sagar Chakraborty, ``On the applicability of low-dimensional models for convective flow reversals at extreme Prandtl numbers'', \doi{10.1140/epjb/e2017-80391-1}{Eur.~Phys.~J.~B~\textbf{90}, 259~(2017)}, \arxiv{1711.01510}{physics.flu-dyn}.
  \item[3.] \bname, Himanshu Gupta, and Sagar Chakraborty, ``Revisiting Evidence of Chaos in X-ray Light Curves: The Case of GRS~1915+105'', \doi{10.3847/1538-4357/833/2/208}{Astrophys.~J.~\textbf{833}, 208~(2016)}, \arxiv{1611.02264}{astro-ph.HE}.
  \item[2.] Aditya Tandon, Malte Schr\"{o}der, \bname, Marc Timme, and Sagar Chakraborty, ``Synchronizing noisy nonidentical oscillators by transient uncoupling'', \doi{10.1063/1.4959141}{Chaos \textbf{26}, 094817~(2016)}, \arxiv{1611.02298}{nlin.CD}.
  \item[1.] Malte Schr\"{o}der, \bname, Debabrata Dutta, Sagar Chakraborty, and Marc Timme, ``Transient Uncoupling Induces Synchronization'', \doi{10.1103/PhysRevLett.115.054101}{Phys.~Rev.~Lett.~\textbf{115}, 054101~(2015)}, \arxiv{1508.06545}{nlin.CD}.
\end{flexlabelled}

\subsection{Scientific software}

\begin{flexlabelled}{hfill}{1.5em}{*}{*}{2.5em}{*}
  \setlength{\itemsep}{0pt}
  \item[1.] \href{https://github.com/manu-mannattil/NoLiTSA}{NoLiTSA} is a Python module for nonlinear time series analysis that I developed between 2015 and 2017.  It has now been used in over 15 scientific publications, and has over 100 stars on GitHub.
\end{flexlabelled}

% Awards and Honors {{{1
% ----------------------

\section{Awards and Honors}

Harry Bloomfield Postdoctoral Fellowship, Tel Aviv University, October 2023.

College of Arts \& Sciences Award, Syracuse University, May 2020.

Fellowship from the Henry Levinstein fund, Department of Physics, Syracuse University, April 2018.

Kishore Vaigyanik Protsahan Yojana, Department of Science and Technology, Government of India, March 2011.

% Talks {{{1
% ----------

\section{Talks and Posters}

Asymptotics, Geometry, and Soft Matter: Tel Aviv University, March 2023; Georgia Institute of Technology, March 2023; Universit\'{e} Paris-Saclay, March 2023.

Can One Hear the Shape of a Filament?: APS March Meeting '23.

Thermal Fluctuations of Singular Bar-Joint Mechanisms: APS March Meetings '21 and '22; Simons Center for Geometry and Physics, Stony Brook University, May 2022.

Introduction to Nonlinear Time Series Analysis: Indian Institute of Technology Kanpur, August 2015.

% Service {{{1
% ------------

\nohangpars

\section{Service to Profession}

Manuscript reviewer for \emph{Physics of Fluids}.

% Teaching {{{1
% -------------

\section{Teaching Experience}

\subsection{Syracuse University}

Instructor for PHY 212 (Electricity \& Magnetism); Grader for PHY 731 (Graduate Statistical Mechanics); Teaching Assistant for PHY 215 (Honors Mechanics), PHY 211 (General Mechanics), PHY 222 (Electricity \& Magnetism Lab), and AST 101 (Introductory Astronomy).

% Miscellaneous {{{1
% ------------------

\section{Miscellaneous}

\hangpars

\emph{Languages.---} English (fluent), Hindi (basic), and Malayalam (native).

\emph{Computer skills.---} Experience writing well-documented and modular software in Python, C++, Mathematica, Vim script, AWK, and various shells (Bash, POSIX sh, etc.); seasoned user of Unix-like operating systems and related software.

% References {{{1
% ---------------

% \section{References}
%
% \begin{minipage}[t]{0.28\textwidth}
%   \begin{tabular}{@{}l}
%   Christian D.~Santangelo\\
%   Department of Physics\\
%   Syracuse University\\
%   \email{cdsantan@syr.edu}
%   \end{tabular}
% \end{minipage}
% %
% \begin{minipage}[t]{0.28\textwidth}
%   \begin{tabular}{@{}l}
%   Jennifer M.~Schwarz\\
%   Department of Physics\\
%   Syracuse University\\
%   \email{jmschwa02@syr.edu}
%   \end{tabular}
% \end{minipage}
% %
% \begin{minipage}[t]{0.28\textwidth}
%   \begin{tabular}{@{}l}
%   Sagar Chakraborty\\
%   Department of Physics\\
%   Indian Insitute of Technology Kanpur\\
%   \email{sagarc@iitk.ac.in}
%   \end{tabular}
% \end{minipage}

% Revision Information {{{1
% -------------------------

\bigskip

\begin{center}
  \color{gray}
  Git commit \href{https://github.com/manu-mannattil/vitae/tree/\gitHash}{\texttt{\gitShortHash}}; \gitCommitterDate
\end{center}

\end{document}
